---
title: "celebrity-association-questionnaire-analysis-CLEAN"
author: "Erin Crandell"
date: "2026-04-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Strating
```{r}
library(dplyr)
library(tidyr)
library(knitr)
data <- read_excel('./Responses.xlsx')
```

# Hypothesis 1. (RQ 1)
Is there an association between celebrity association with a beauty product and consumers’ purchase intention?

# Renaming Data
```{r}
data <- data %>%
  rename(
    Q8  = `8. I am more interested in a beauty product if it is associated with a celebrity.`,
    Q10 = `10. Celebrity involvement makes a product more appealing.`,
    Q13 = `13. I am likely to purchase a beauty product endorsed by a celebrity.`)

```
# Variable Construction
```{r}
data <- data %>%
  mutate(
    celebrity_association = rowMeans(select(.,Q8,Q10), na.rm = TRUE), purchase_intention = rowMeans(select(.,Q13), na.rm = TRUE)
)
```

# Table Visualistion for RQ1.
```{r}
table_data <- data %>%
  select(Q8, Q10, Q13) %>%
  pivot_longer(cols = everything(),
    names_to  = "Question",
    values_to = "Response") %>%
  mutate(Response = factor(Response,
      levels = 1:5,
      labels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"))) %>%
  group_by(Question, Response) %>%
  summarise(n = n(), .groups = "drop") %>%
  pivot_wider(names_from  = Response, values_from = n) %>%
    arrange(match(Question, c("Q8", "Q10", "Q13")))

totals_row <- table_data %>%
  summarise(across(where(is.numeric), sum)) %>%
  mutate(Question = "Total")

bind_rows(table_data, totals_row) %>%
  kable(caption = "Answers: Perceived Celebrity Association and Purchase Intention")
```

# Multicollinearity Visualisation for RQ1.
```{r}
library(ggplot2)
ggplot(data, aes(x = celebrity_association, y = purchase_intention)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    title = "Celebrity Association and Purchase Intention",
    x = "Celebrity Association",
    y = "Purchase Intention"
  )+
  theme_minimal()
```
# RQ 1. Spearman test
```{r}
cor.test(data$celebrity_association,
         data$purchase_intention,
         method = "spearman")

options(scipen = 999)
```
#Findings for RQ 1.
We found that celebrity association with beauty products is positively associated with consumers' purchase intention, ρ = 0.69, p < 0.001.

#Hypothesis 2. (RQ 2) 
What perceived factors are most influential in consumer behavior? 

# Bar Chart Visualisation for RQ 2.
```{r}
data <- data %>%
  rename(
    Q12 = `12. Of the following factors, which factor would you say influences your purchase decision the most?`)

data_q12 <- data %>%
  select(Q12) %>%
  filter(!is.na(Q12)) %>%
  mutate(
    Q12 = factor(Q12,
      levels = c(
        "Trustworthiness",
        "Expertise",
        "Authenticity",
        "Physical attractiveness",
        "Celebrity status"
      )
    )
  )

data_count <- data_q12 %>%
  count(Q12)

ggplot(data_count, aes(x = reorder(Q12, n), y = n)) +
  geom_col(fill = "skyblue") +
  labs(
    title = "Most Influential Factor in Purchase Decision",
    x = "Factor",
    y = "Count"
  ) +
  coord_flip() +
  theme_minimal()
```

# Table Visualisation for RQ 2. 
```{r}
# 4. Make frequency table
Q12_table <- data_q12 %>%
count(Q12) %>%
mutate(
Percent = round(n / sum(n) * 100, 1)
) %>%
rename(
Factor = Q12,
Count = n
)

# 5. View table
Q12_table
```

# Findings for RQ 2.
We found that consumers perceived trustworthiness is the most influential factor, followed by expertise, while authenticity, physical attractiveness and celebrity status exert much weaker impacts on consumers’ purchase behaviours.


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
