---
title: "Test"
author: "nicky8933"
date: "2026-04-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(readr)
library(ggplot2)

options(scipen = 999)

data <- read_csv('../data/celebrity-association-questionnaire-responses-4.26.csv')
```

# Hypothesis 1.
Is there an association between celebrity association with a beauty product and consumers’ purchase intention?

```{r}
data <- data %>%
  rename(
    Q8  = '8. I am more interested in a beauty product if it is associated with a celebrity.',
    Q10 = '10. Celebrity involvement makes a product more appealing.',
    Q13 = '13. I am likely to purchase a beauty product endorsed by a celebrity.')
```

```{r}
data <- data %>%
  mutate(
    celebrity_association = rowMeans(select(.,Q8,Q10), na.rm = TRUE), purchase_intention = rowMeans(select(.,Q13), na.rm = TRUE)
  )
```

```{r}
library(ggplot2)
ggplot(data, aes(x = celebrity_association, y = purchase_intention)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    title = "Perceived Celebrity Association and Purchase Intention",
    x = "Perceived Celebrity Association (Low to High)",
    y = "Purchase Intention (Low to High)"
  )+
  theme_minimal()
```
```{r}
cor.test(data$celebrity_association,
         data$purchase_intention,
         method = "spearman",
         exact = FALSE)

```

#Finding1
A Spearman rank correlation indicated that perceived celebrity association is positively associated with purchase intention, rs(148) = .69, p < .001.

##ERIN TESTING##

#Analysis 2: Chi-square test with Questions 8 and 13, correlation between perceived celebrity association with a beauty product and purchase intention.

```{r}
library(dplyr)

data <- data %>%
  mutate(
    Q8_cat = case_when(
      Q8 %in% c(1, 2) ~ "Disagree",
      Q8 == 3         ~ "Neutral",
      Q8 %in% c(4, 5) ~ "Agree"
    ),
    Q13_cat = case_when(
      Q13 %in% c(1, 2) ~ "Disagree",
      Q13 == 3         ~ "Neutral",
      Q13 %in% c(4, 5) ~ "Agree"
    )
  )

likert_levels <- c("Disagree", "Neutral", "Agree")

data <- data %>%
  mutate(
    Q8_cat = factor(Q8_cat, levels = likert_levels),
    Q13_cat = factor(Q13_cat, levels = likert_levels)
  )

table(data$Q8, 
      data$Q8_cat, 
      useNA = NULL)

chisq.test(data$Q8_cat, 
           data$Q13_cat)
```
#Finding: Perceived celebrity association is associated with purchase intention, X2(df = 4, n = 148) = 70.719 with a p-value of < 0.001.
##Note: Almost half of respondants were "Neutral"

```{r}
library(dplyr)
library(tidyr)
library(knitr)

names(data)

table_data <- data %>%
  select(Q8, Q10, Q13) %>%
  pivot_longer(cols = everything(),
    names_to  = "Question",
    values_to = "Response") %>%
  mutate(Response = factor(Response,
      levels = 1:5,
      labels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"))) %>%
  group_by(Question, Response) %>%
  summarise(n = n(), .groups = "drop") %>%
  pivot_wider(names_from  = Response, values_from = n) %>%
    arrange(match(Question, c("Q8", "Q10", "Q13")))

totals_row <- table_data %>%
  summarise(across(where(is.numeric), sum)) %>%
  mutate(Question = "Total")

bind_rows(table_data, totals_row) %>%
  kable(caption = "Answers: Perceived Celebrity Association and Purchase Intention")
```
